Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-12-04 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
xxxxx papperrrr

# 4. Format t-Test and Cohen's d Results for APA Table
t_test_result <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_letter$statistic, 2),
  "df" = t_test_letter$parameter,
  "p-value" = format.pval(t_test_letter$p.value, digits = 3, eps = .001),
  "Mean Difference" = round(t_test_letter$estimate[1] - t_test_letter$estimate[2], 2),
  "Cohen's d" = round(d_letter$estimate, 2),
  "95% CI (d)" = paste0("[", round(d_letter$conf.int[1], 2), ", ", round(d_letter$conf.int[2], 2), "]")
)

@@

      # Format the results for the current AOI and add to the results data frame
      results <- rbind(
        results,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = round(t_test_result$statistic, 2),
          "df" = t_test_result$parameter,
          "p-value" = format.pval(t_test_result$p.value, digits = 3, eps = .001),
          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
          "Cohen's d" = round(cohen_d_value, 2),
          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
        )
      )

@@

# 4. Perform t-test to get the p-value
t_test_mtu <- t.test(
  Number_fixation_min_mtu ~ Group,
  data = df_aoi_sum,
  var.equal = TRUE
)
p_value_mtu <- round(t_test_mtu$p.value, 3)

@@

# 7. Format the t-Test and Cohen's d results for APA Table
t_test_result <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_mtu$statistic, 2),
  "df" = t_test_mtu$parameter,
  "p-value" = format.pval(t_test_mtu$p.value, digits = 3, eps = .001),
  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
  "Cohen's d" = cohen_d_mtu,
  "95% CI (d)" = paste0("[", round(t_test_mtu$conf.int[1], 2), ", ", round(t_test_mtu$conf.int[2], 2), "]")
)

@@

# Extract statistical values
mean_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(M)
sd_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(SD)
mean_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(M)
sd_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(SD)
p_value <- format.pval(t_test_stud$p.value, digits = 3, eps = .001)
cohen_d <- round(d_number_stud$estimate, 2)

@@

# 5. Format t-Test and Cohen's d Results for APA Table
t_test_result_stud <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_stud$statistic, 2),
  "df" = t_test_stud$parameter,
  "p-value" = format.pval(t_test_stud$p.value, digits = 3, eps = .001),
  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
  "Cohen's d" = round(d_number_stud$estimate, 2),
  "95% CI (d)" = paste0("[", round(d_number_stud$conf.int[1], 2), ", ", round(d_number_stud$conf.int[2], 2), "]")
)

@@

# t-Test and effect size
t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
p_value <- round(t_test$p.value, 3)
cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)

@@

# Post-hoc comparisons for Disruption_Category
post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)

# Extract pairwise contrasts
post_hoc_results <- as.data.frame(post_hoc_disruption$contrasts)

# Clean up category names in the contrast column
post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast)
post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast)

# Calculate Cohen's d for each pairwise comparison using pooled SD from emmeans
post_hoc_results <- post_hoc_results %>%
  mutate(
    pooled_sd = sqrt((SE^2 * 2)), # Approximation for pooled SD from SE
    d = round(estimate / pooled_sd, 2), # Calculate Cohen's d
    p.value = ifelse(
      p.value < 0.05, "< .05", round(p.value, 3)
    ),
    t = round(t.ratio, 2),
    df = round(df, 2),
    Estimate = round(estimate, 2),
    SE = round(SE, 2)
  ) %>%
  select(contrast, Estimate, SE, df, t, p.value, d) # Include Cohen's d

# Display APA-styled post-hoc table
kable(
  post_hoc_results,
  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
  digits = 2
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

# Plot 2: Disruption Duration by Group and Category
plot_duration_category <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
  geom_boxplot(outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
  labs(x = "Group", y = "Disruption Duration (seconds)") +
  theme_cowplot() +
  ylim(0, 30) + 
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Disruption Duration by Group and Category") +
  theme(legend.position = "none")

plot_duration_category

@@

# 1. Normality Tests (Shapiro-Wilk)
# The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
normality_tests <- df_aoi_disrup %>%
  group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
  summarise(
    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
    .groups = "drop"  # Drop the grouping after summarizing
  )

# The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution. This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.

# Display the Shapiro-Wilk test results in a nicely formatted table
kable(
  normality_tests,  # Table with Shapiro-Wilk p-values for each group
  caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
  col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern

# 2. Mann-Whitney U-Test and Effect Size
# The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
# This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)

# Calculate Effect Size (r) for the Mann-Whitney U test
# Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)

# Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
mann_whitney_results <- data.frame(
  "Test" = "Mann-Whitney U",  # Test name
  "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
  "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
  "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
)

# Display the Mann-Whitney U test results in a formatted table
kable(
  mann_whitney_results,
  caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

# 3. Kruskal-Wallis Test and Pairwise Comparisons
# The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
# It tests whether the distributions of disruption duration across categories are equal.
kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)

# Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
kruskal_results <- data.frame(
  "Test" = "Kruskal-Wallis",  # Test name
  "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
  "df" = kruskal_test$parameter,  # Degrees of freedom (df)
  "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
)

# Display the Kruskal-Wallis test results in a formatted table
kable(
  kruskal_results,
  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

# 4. Pairwise Wilcoxon test with Bonferroni correction
# The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
# The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
pairwise_wilcox <- pairwise.wilcox.test(
  x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
  g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
  p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
)

# Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
  mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals

# Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
kable(
  pairwise_results,
  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
  row.names = TRUE  # Display row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

>>>>

# 4. Format t-Test and Cohen's d Results for APA Table
t_test_result <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_letter$statistic, 2),
  "df" = t_test_letter$parameter,
  "p-value" = format.pval(t_test_letter$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_letter$estimate[1] - t_test_letter$estimate[2], 2),
  "Cohen's d" = round(d_letter$estimate, 2),
  "95% CI (d)" = paste0("[", round(d_letter$conf.int[1], 2), ", ", round(d_letter$conf.int[2], 2), "]")
)

@@

      # Format the results for the current AOI and add to the results data frame
      results <- rbind(
        results,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = round(t_test_result$statistic, 2),
          "df" = t_test_result$parameter,
          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
          "Cohen's d" = round(cohen_d_value, 2),
          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
        )
      )

@@

# 4. Perform t-test to get the p-value
t_test_mtu <- t.test(
  Number_fixation_min_mtu ~ Group,
  data = df_aoi_sum,
  var.equal = TRUE
)
p_value_mtu <- round(t_test_mtu$p.value, 2)

@@

# 7. Format the t-Test and Cohen's d results for APA Table
t_test_result <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_mtu$statistic, 2),
  "df" = t_test_mtu$parameter,
  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
  "Cohen's d" = cohen_d_mtu,
  "95% CI (d)" = paste0("[", round(t_test_mtu$conf.int[1], 2), ", ", round(t_test_mtu$conf.int[2], 2), "]")
)

@@

# Extract statistical values
mean_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(M)
sd_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(SD)
mean_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(M)
sd_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(SD)
p_value <- format.pval(t_test_stud$p.value, digits = 2, eps = .05)
cohen_d <- round(d_number_stud$estimate, 2)

@@

# 5. Format t-Test and Cohen's d Results for APA Table
t_test_result_stud <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_stud$statistic, 2),
  "df" = t_test_stud$parameter,
  "p-value" = format.pval(t_test_stud$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
  "Cohen's d" = round(d_number_stud$estimate, 2),
  "95% CI (d)" = paste0("[", round(d_number_stud$conf.int[1], 2), ", ", round(d_number_stud$conf.int[2], 2), "]")
)

@@

# t-Test and effect size
t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
p_value <- round(t_test$p.value, 2)
cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)

@@

# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)

# Extract post-hoc pairwise contrasts for Disruption_Category
post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
  mutate(
    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
    Estimate = round(estimate, 2),
    SE = round(SE, 2),
    t = round(t.ratio, 2),
    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
  )

##################### COHEN'S D CALCULATION ########################

# Define the disruption categories
categories <- c("Lack of eagerness to learn", "Physical disruptions", "Verbal disruptions")

# Initialize an empty list to store the Cohen's d values
cohen_d_values <- vector("list", length = nrow(post_hoc_results_disruption))

# Loop over the post-hoc results to calculate Cohen's d for each comparison
for (i in 1:nrow(post_hoc_results_disruption)) {
  # Extract the two categories being compared
  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]

  # Get the data for the two groups being compared using fixations_per_second
  group1_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group1]
  group2_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group2]

  # Calculate the means and standard deviations for each group
  mean1 <- mean(group1_data, na.rm = TRUE)
  mean2 <- mean(group2_data, na.rm = TRUE)

  sd1 <- sd(group1_data, na.rm = TRUE)
  sd2 <- sd(group2_data, na.rm = TRUE)

  # Calculate the pooled standard deviation
  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))

  # Calculate Cohen's d using the formula (mean difference / pooled SD)
  d_value <- (mean1 - mean2) / pooled_sd

  # Store the absolute value of Cohen's d
  cohen_d_values[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
}

# Add the Cohen's d values to the post-hoc results
post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values)

# Ensure the number of column names matches the number of columns in the data frame
post_hoc_results_disruption <- post_hoc_results_disruption %>%
  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)

# Displaying the table
knitr::kable(
  post_hoc_results_disruption,
  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
  digits = 2
) %>%
kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# # effect size for category differences
# d_fix_disrup <- CohenD(
#   x = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Lack of eagerness to learn"],
#   y = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Verbal disruptions"],
#   na.rm = TRUE
# )
# 
# round(d_fix_disrup, 2)

@@

# Plot 2: Disruption Duration by Group and Category
plot_duration_category <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
  geom_boxplot(outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets
  labs(x = "Group", y = "Disruption Duration (seconds)") +
  theme_cowplot() +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Disruption Duration by Group and Category") +
  theme(legend.position = "none")

# Display the plot
plot_duration_category

@@

# Perform the repeated-measures ANOVA with `Duration_of_interval_sec` as the dependent variable
anova_afex_duration <- afex::aov_ez(
  id = "Participant",  # Random effect
  dv = "Duration_of_interval_sec",  # Dependent variable: disruption duration in seconds
  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
  within = "Disruption_Category",  # Within-subject factor: Disruption Categories
  data = df_aoi_disrup
)

# Extract the ANOVA table
anova_results_duration <- as.data.frame(anova_afex_duration$anova_table)

# Recalculate generalized eta squared (η²) for effect size
eta_squared_results_duration <- effectsize::eta_squared(anova_afex_duration, partial = FALSE)

# Combine recalculated eta squared with the ANOVA table
anova_table_apa_duration <- anova_results_duration %>%
  rownames_to_column(var = "Effect") %>%  # Move row names to a column
  left_join(
    as.data.frame(eta_squared_results_duration), 
    by = c("Effect" = "Parameter")  # Match the correct columns
  ) %>%
  mutate(
    `F` = round(`F`, 2),  # Round F-values
    `η²` = round(Eta2, 3),  # Round generalized eta squared
    `p-value` = ifelse(
      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3)  # Format p-values
    )
  ) %>%
  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last

# Display the ANOVA table
kable(
  anova_table_apa_duration,
  caption = "Repeated-Measures ANOVA Results for Disruption Duration (Including Effect Sizes)",
  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
  digits = 2
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

##################### POST-HOC TESTS Disruption_Category (main effect) ########################

# Perform post-hoc pairwise comparisons for Disruption_Category (main effect)
post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)

# Extract post-hoc pairwise contrasts for Disruption_Category (main effect)
post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
  mutate(
    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
    Estimate = round(estimate, 2),
    SE = round(SE, 2),
    t = round(t.ratio, 2),
    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
  )

##################### COHEN'S D CALCULATION ########################

# Initialize empty lists to store Cohen's d values for both post-hoc tests
cohen_d_values_disruption <- vector("list", length = nrow(post_hoc_results_disruption))

# Loop over the post-hoc results for Disruption_Category to calculate Cohen's d for each comparison (main effect)
for (i in 1:nrow(post_hoc_results_disruption)) {
  # Extract the two categories being compared
  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]

  # Get the data for the two groups being compared using Duration_of_interval_sec
  group1_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group1]
  group2_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group2]

  # Calculate the means and standard deviations for each group
  mean1 <- mean(group1_data, na.rm = TRUE)
  mean2 <- mean(group2_data, na.rm = TRUE)

  sd1 <- sd(group1_data, na.rm = TRUE)
  sd2 <- sd(group2_data, na.rm = TRUE)

  # Calculate the pooled standard deviation
  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))

  # Calculate Cohen's d using the formula (mean difference / pooled SD)
  d_value <- (mean1 - mean2) / pooled_sd

  # Store the absolute value of Cohen's d
  cohen_d_values_disruption[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
}

# Add the Cohen's d values to the post-hoc results
post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values_disruption)

# Ensure the number of column names matches the number of columns in the data frame
post_hoc_results_disruption <- post_hoc_results_disruption %>%
  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)

# Displaying the post-hoc results for Disruption Category (main effect)
knitr::kable(
  post_hoc_results_disruption,
  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Main Effect)",
  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
  digits = 2
) %>%
kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

#################### POST-HOC TESTS interaction effect (Group:Disruption_Category) ########################

# Calculate post-hoc pairwise comparisons for the interaction effect (Group:Disruption_Category)
post_hoc_interaction <- emmeans(anova_afex, pairwise ~ Group * Disruption_Category)

# Extract the post-hoc contrasts for the interaction
post_hoc_results_interaction <- as.data.frame(post_hoc_interaction$contrasts) %>%
  mutate(
    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
    Estimate = round(estimate, 2),
    SE = round(SE, 2),
    t = round(t.ratio, 2),
    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
  )

##################### COHEN'S D CALCULATION ########################

# 1. Novice Lack of eagerness to learn vs Expert Lack of eagerness to learn
d_LackOfEagerness_Novice_vs_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  na.rm = TRUE
)

# 2. Novice Lack of eagerness to learn vs Novice Physical disruptions
d_LackOfEagerness_vs_Physical_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  na.rm = TRUE
)

# 3. Novice Lack of eagerness to learn vs Expert Physical disruptions
d_LackOfEagerness_vs_Physical_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  na.rm = TRUE
)

# 4. Novice Lack of eagerness to learn vs Novice Verbal disruptions
d_LackOfEagerness_vs_Verbal_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 5. Novice Lack of eagerness to learn vs Expert Verbal disruptions
d_LackOfEagerness_vs_Verbal_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 6. Expert Lack of eagerness to learn vs Novice Physical disruptions
d_Expert_LackOfEagerness_vs_Physical_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  na.rm = TRUE
)

# 7. Expert Lack of eagerness to learn vs Expert Physical disruptions
d_Expert_LackOfEagerness_vs_Physical_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  na.rm = TRUE
)

# 8. Expert Lack of eagerness to learn vs Novice Verbal disruptions
d_Expert_LackOfEagerness_vs_Verbal_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 9. Expert Lack of eagerness to learn vs Expert Verbal disruptions
d_Expert_LackOfEagerness_vs_Verbal_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 10. Novice Physical disruptions vs Expert Physical disruptions
d_Physical_Novice_vs_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  na.rm = TRUE
)

# 11. Novice Physical disruptions vs Novice Verbal disruptions
d_Physical_Novice_vs_Verbal_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 12. Novice Physical disruptions vs Expert Verbal disruptions
d_Physical_Novice_vs_Verbal_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 13. Expert Physical disruptions vs Novice Verbal disruptions
d_Physical_Expert_vs_Verbal_Novice <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 14. Expert Physical disruptions vs Expert Verbal disruptions
d_Physical_Expert_vs_Verbal_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

# 15. Novice Verbal disruptions vs Expert Verbal disruptions
d_Verbal_Novice_vs_Expert <- CohenD(
  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
  na.rm = TRUE
)

##################### CREATE A NAMED VECTOR FOR COHEN'S D ########################

# Create a named vector with the correct Cohen's d values
cohen_d_values_interaction <- c(
  "Novice Lack of eagerness to learn - Expert Lack of eagerness to learn" = round(d_LackOfEagerness_Novice_vs_Expert, 2),
  "Novice Lack of eagerness to learn - Novice Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Novice, 2),
  "Novice Lack of eagerness to learn - Expert Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Expert, 2),
  "Novice Lack of eagerness to learn - Novice Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Novice, 2),
  "Novice Lack of eagerness to learn - Expert Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Expert, 2),
  "Expert Lack of eagerness to learn - Novice Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Novice, 2),
  "Expert Lack of eagerness to learn - Expert Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Expert, 2),
  "Expert Lack of eagerness to learn - Novice Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Novice, 2),
  "Expert Lack of eagerness to learn - Expert Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Expert, 2),
  "Novice Physical disruptions - Expert Physical disruptions" = round(d_Physical_Novice_vs_Expert, 2),
  "Novice Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Novice, 2),
  "Novice Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Expert, 2),
  "Expert Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Novice, 2),
  "Expert Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Expert, 2),
  "Novice Verbal disruptions - Expert Verbal disruptions" = round(d_Verbal_Novice_vs_Expert, 2)
)

##################### ADD COHEN'S D VALUES TO THE POST-HOC RESULTS ########################

# Add Cohen's d values to the post-hoc results for each comparison
post_hoc_results_interaction$Cohen_d <- cohen_d_values_interaction[post_hoc_results_interaction$Comparison]

##################### TABLE FOR INTERACTION EFFECT ########################

# Ensure the number of column names matches the number of columns in the data frame
post_hoc_results_interaction <- post_hoc_results_interaction %>%
  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
